### 2014-05-09 Thesis/Latex/hfdst-sensamp.tex
SA-hoofdstuk extra tabel gemaakt

>>>>

\begin{table}
\begin{tabular}{cccccc}
\hline 
Transistor & Parameter & Richtingscoëfficiënt [$\frac{mV}{\sigma}$] & W [nm] & L [nm] & $\sigma$ \\ 
\hline 
Mup & Vt & -4.283 & 1700 & 45 & 9.0388mV \\ 
Mupbar & Vt & 4.283 & 1700 & 45 & 9.0388mV \\ 
Mpassn & Vt & -3.767 & 500 & 45 & 18.8000mV \\
Mpassbarn & Vt & 3.650 & 500 & 45 & 18.8000mV \\
Mpassbarn & $\beta$ & -3.000 & 500 & 45 & 13.3333\% \\ 
Mpassn & $\beta$ & 3.000 & 500 & 45 & 13.3333\% \\ 
Mup & $\beta$ & -1.767 & 1700 & 45 & 4.3386\% \\ 
Mupbar & $\beta$ & 1.767 & 1700 & 45 & 4.3386\% \\ 
Mdown & Vt & -1.100 & 1500 & 45 & 10.8542mV \\ 
Mdownbar & Vt & 1.100 & 1500 & 45 & 10.8542mV \\
Mdown & $\beta$ & 0.8333 & 1500 & 45 & 7.6980\% \\
Mdownbar & $\beta$ & -0.8333 & 1500 & 45 & 7.6980\% \\  
Mpassp & Vt & 0.1667 & 500 & 45 & 16.6667mV \\ 
Mpassp & $\beta$ & 0.1667 & 500 & 45 & 8\% \\ 
Mpassbarp & Vt & -0.1667 & 500 & 45 & 16.6667mV \\
Mpassbarp & $\beta$ & -0.1667 & 500 & 45 & 8\% \\ 
Mtop & $\beta$ & 0.1333 & 900 & 45 & 5.9628\% \\ 
Mtop & Vt & 0.1000 & 900 & 45 & 12.4226mV \\ 
Mbottom & $\beta$ & -0.06667 & 500 & 45 & 13.3333\% \\ 
Mbottom & Vt & 0.03333 & 500 & 45 & 18.8000mV \\ 
\hline 
\hline & $\sigma_{Voffset}$: & 9.6125mV & & & \\
\hline
\end{tabular} 
\caption{Sensitiviteitsanalyse van de SA in het finale geheugen, er is overlap tussen de controlesignalen}
\label{tab:ourSA-sensanalysis-overlap}
\end{table}
